---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# electionsFR

<!-- badges: start -->
<!-- badges: end -->

The goal of electionsFR is to offer a set of functions to easily download and clean French electoral data from the public archive data-gouv.fr \url{https://www.data.gouv.fr/fr/organizations/ministere-de-l-interieur/}.

## Installation

You can install the development version of electionsFR from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("FredCassor/electionsFR")
```

## Example

This is a basic example which shows you how to get the datasets ressources released by the French Ministry of the Interior, available online:

```{r example}
library(electionsFR)
data("ressources")
colnames(ressources)
```

This is an example which shows you how to access datasets which refer to the Presidential election in 2002:
```{r president, message=FALSE, warning=FALSE}
library(dplyr)
library(stringi)
ressources |> 
   mutate(dataset_title = stri_trans_general(dataset.title, "Latin-ASCII")) |> 
   filter(grepl("election presidentielle", dataset_title, ignore.case = TRUE)) |> 
   filter(annee == 2002) |> 
   select(dataset.title, downloads)
```

