---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# electionsFR

<!-- badges: start -->
<!-- badges: end -->

The goal of electionsFR is to offer a set of functions to easily download and clean French electoral data from the public archive data-gouv.fr \url{https://www.data.gouv.fr/fr/organizations/ministere-de-l-interieur/}.

## Installation

You can install the development version of electionsFR from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("FredCassor/electionsFR")
```

## Examples

### Presidential election data

This is a basic example which shows you how to download datasets which refer to the Presidential election in 2002, published by the French Ministry of the Interior:
```{r ex-president, eval=FALSE}
library(electionsFR)
get_presidentielle(2002)
```

### General elections

For getting data on general elections, this is an example of downloading files on general elections in 2007 and saved in the sub directory `elections`: 
```{r general-election, eval=FALSE}
get_legislatives(2007, exdir = "elections")
```

