---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# electionsFR

<!-- badges: start -->
<!-- badges: end -->

The main goal of electionsFR is to offer a set of functions to easily download and clean French electoral data from the public archive data-gouv.fr \url{https://www.data.gouv.fr/fr/organizations/ministere-de-l-interieur/}.

## Installation

You can install the development version of electionsFR from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("FredCassor/electionsFR")
```

## Examples

### Year of election

This table is a reminder of possible values for year of each election that took place in France. This may be useful when we want to download files on election.

| Elections | Year |
| ----| ---- |
| Election présidentielle | 1995, 2002, 2007, 2012, 2017, 2022 |
| Elections législatives | 1993, 1997, 2002, 2007, 2012, 2016, 2017, 2022, 2024 |
| Elections européennes | 1994, 1999, 2004, 2009, 2014, 2019, 2024 |
| Elections régionales | 1998, 2004, 2010, 2015, 2021 |
| Elections départementales | 2015, 2021 |
| Elections cantonales | 1992, 1994, 1998, 2001, 2004, 2008, 2011 |
| Elections municipales | 2001, 2008, 2014, 2015, 2020, 2026 |
| Elections sénatoriales | 1992, 1995, 1998, 2001, 2004, 2008, 2011, 2014, 2015, 2017, 2023, 2026 |
| Référendum | 1992, 2000, 2005, 2013 |

### Presidential election data

This is a basic example which shows you how to download files which refer to the Presidential election in 2002, published by the French Ministry of the Interior:
```{r ex-president, eval=FALSE}
library(electionsFR)
get_presidentielle(2002)
```

### General elections

For getting data on general elections, this is an example of downloading files on general elections in 2007 and saved in the sub directory `elections`: 
```{r general-election, eval=FALSE}
get_legislatives(2007, exdir = "elections")
```

